---
title: "v2progress"
output:
  html_document: default
  html_notebook: default
---

Import dataset from: [link](https://www.kaggle.com/kevinmh/fifa-18-more-complete-player-dataset)

```{r}
suppressWarnings(library(readr))
suppressWarnings(library(tidyverse))
complete <- read_csv("~/R/r4ds/soccer/complete.csv")
```
make subsets of data
```{r}
complete[1:15]
table(complete$international_reputation)
ggplot(data = complete) + 
  geom_bar(mapping = aes(x = international_reputation))
```

```{r}
dplyr::mutate(complete, bmi = height_cm/weight_kg)
stars <- filter(complete, international_reputation>2)
super_star <- filter(stars, international_reputation>3)
rmd <- filter(complete, club == "Real Madrid CF")
barc <- filter(complete, club == "FC Barcelona")
data.combined <- rbind(rmd, barc)%>%
  select(name, age, league, body_type)
```
apply to all skills in dataset to see which have large positive or negative correlations
```{r}
skills <- select(complete, 34:67)%>%
  cor()%>%
  as_tibble
  mutate(skills, skill = colnames(skills))
```
Table finds which skills are most correlated with each other. 
```{r}
ability <- select(complete, overall, ball_control, gk_diving, dribbling, penalties, positioning)
cor(ability)%>%
as_tibble()
#use random sample or visualization will be a bunch of blobs
  slice(ability, sample(1:17994, 100, replace = FALSE))%>%
  pairs()


```
Those who are good at positionig and ball control have higher overall socres. Goal kick diving correlates with lower scores. 

```{r}
ggplot(data = complete) + 
  geom_point(mapping = aes(x = height_cm, y = weight_kg, color = body_type))+
  labs(x = "Height", y = "Weight", title = "Height and Weight Range by Body Type", color = "Body Type")

```
Wage vs international reputation

```{r}
  ggplot(data = complete) +
  geom_point(mapping = aes(x = international_reputation, y = eur_wage))
```
value, potential, overall, wage
```{r}
ggplot(data = complete) +
  geom_point(mapping = aes(x = potential, y = eur_wage))
ggplot(data = complete) +
  geom_point(mapping = aes(x = eur_value, y = eur_wage))
ggplot(data = complete) +
  geom_point(mapping = aes(x = overall, y = eur_wage))
ggplot(data = complete) +
  geom_point(mapping = aes(x = eur_wage, y = age))
```
take out 0 wage values and add column value for continent
```{r}
nozero <- filter(complete, eur_wage > 999, nationality != "São Tomé & Príncipe")
Africa<-c('Algeria','Angola','Benin','Botswana','Burkina','Burundi','Cameroon','Cape Verde','Central African Republic','Chad','Comoros','Congo','Congo Democratic Republic of','Djibouti','Egypt','Equatorial Guinea','Eritrea','Ethiopia','Central African Rep.','DR Congo','Gabon','Gambia','Ghana','Guinea','Guinea Bissau','Guinea-Bissau','Ivory Coast','Kenya','Lesotho','Liberia','Libya','Madagascar','Malawi','Mali','Mauritania','Mauritius','Morocco','Mozambique','Namibia','Niger','Nigeria','Rwanda','S?o Tom? & Pr?ncipe','Sao Tome and Principe','Senegal','Seychelles','Sierra Leone','Somalia','South Africa','South Sudan','Sudan','Swaziland','Tanzania','Togo','Tunisia','Uganda','Zambia','Zimbabwe','Burkina Faso')
Oceania<-c('Australia','Guam','New Caldonia', 'Fiji','Kiribati','Marshall Islands','Micronesia','Nauru','New Caledonia','New Zealand','Palau','Papua New Guinea','Samoa','Solomon Islands','Tonga','Tuvalu','Vanuatu')
Asia<-c('Afghanistan','Bahrain','Bangladesh','Bhutan','Brunei','Burma (Myanmar)','Cambodia','China','China PR','East Timor','Hong Kong','India','Indonesia','Iran','Iraq','Israel','Japan','Jordan','Kazakhstan','North Korea','South Korea','Korea DPR','Korea Republic','Kuwait','Kyrgyzstan','Laos','Lebanon','Malaysia','Maldives','Mongolia','Nepal','Oman','Pakistan','Palestine','Philippines','Qatar','Russian Federation','Saudi Arabia','Singapore','Sri Lanka','Syria','Tajikistan','Thailand','Turkey','Turkmenistan','United Arab Emirates','Uzbekistan','Vietnam','Yemen','Russia')
Europe<-c('Albania','Andorra','Armenia','Austria','Azerbaijan','Belarus','Belgium','Bosnia and Herzegovina','Bosnia Herzegovina','Bulgaria','Croatia','Cyprus','Czech Republic','Denmark','Estonia','Faroe Islands','FYR Macedonia','Gibraltar','Finland','France','Georgia','Germany','Greece','Hungary','Iceland','Ireland','Italy','Latvia','Liechtenstein','Kosovo','Lithuania','Luxembourg','Macedonia','Malta','Moldova','Monaco','Montenegro','Netherlands','Northern Ireland','Norway','Poland','Portugal','Romania','San Marino','Scotland','Serbia','Slovakia','Slovenia','Spain','Sweden','Switzerland','Ukraine','England','Vatican City','Republic of Ireland','Wales')
North_america<-c('Antigua and Barbuda','Antigua & Barbuda','Bahamas','Barbados','Belize','Bermuda','Canada','Costa Rica','Cuba','Dominica','Dominican Republic','El Salvador','Grenada','Guatemala','Montserrat','Haiti','Honduras','Jamaica','Mexico','Nicaragua','Panama','Puerto Rico','Saint Kitts and Nevis','Saint Lucia','Saint Vincent and the Grenadines','St Kitts Nevis','St Lucia','Trinidad and Tobago','United States')
South_america<-c('Argentina','Curacao','Bolivia','Brazil','Chile','Colombia','Ecuador','Guyana','Paraguay','Peru','Suriname','Trinidad & Tobago','Uruguay','Venezuela')
nozero$nationality[nozero$nationality %in% Africa] <- "Africa"
nozero$nationality[nozero$nationality %in% Asia] <- "Asia"
nozero$nationality[nozero$nationality %in% Europe] <- "Europe"
nozero$nationality[nozero$nationality %in% North_america] <- "North_america"
nozero$nationality[nozero$nationality %in% South_america]<-"South_america"
nozero$nationality[nozero$nationality %in% Oceania] <- "Oceania"

```

Check for missing countries
```{r}
count(nozero, nationality)
```
Checks out

```{r}
nozero %>%
  group_by(nationality)%>%
  summarize_at(vars(eur_wage, overall), funs(mean,sd))
```

```{r}
mean(complete$eur_wage)
mean(stars$eur_wage)
mean(super_star$eur_wage)
max(complete$eur_wage)
min(complete$eur_wage)
#transmute_at(complete)
```
Why is the median so low?
Hypothesis: players making no wage are young 
```{r}
free <- filter(complete, eur_wage == 0) %>%
  select(full_name, age)
ggplot(data = free)+
  geom_bar(mapping = aes(x = age))
ggplot(data = complete)+
  geom_bar(mapping = aes(x = age))
```
Age is only slightly skewed to younger ages.  
```{r}
ggplot(data = nozero) + 
  geom_point(mapping = aes(x = eur_value, y = overall)) + 
  facet_wrap(~ nationality, nrow = 2) +
  labs(title = "Wage Vs Skill", x = "Wage", ylab = "Skill Score")
```
continent and skill_moves
```{r}
nozero$skill_moves <- as.factor(nozero$skill_moves)
ggplot(data = nozero) + 
  geom_bar(mapping = aes(x = nationality, fill = skill_moves)) +
  labs(x = "Continent",fill = "Ball Handeling")
```
Is this different for elite players?
```{r}
s <- filter(nozero, international_reputation>2)
s$skill_moves <- as.factor(s$skill_moves)
ggplot(data = s) + 
  geom_bar(mapping = aes(x = nationality, fill = skill_moves)) +
  labs(x = "Continent",fill = "Ball Handeling")
```
Scores are higher for this group.
```{r}
ggplot(data = nozero) +
  geom_violin(mapping = aes(x = nationality, y = overall)) +
  coord_flip()+
  xlab("Continent")+
  ylab("Score")
```


